Tables in the project

### 2018-08-02 paper/Chapters/Chapter3.tex
level1 level2 fig added

	\caption{\label{tab:daylevel}Day Level Latent Class Solution for Three-Class Model (No Individual level Model)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{llccccc}
		\hiderowcolors
		\toprule
		\textbf{Time slots of} & \textbf{Responses of} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(30.8\%)}} & \textbf{\Centerstack{Class 2\\(39.8\%)}} & \textbf{\Centerstack{Class 3\\(29.5\%)}} \\
		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Lower carbo-\\hydrate day}} & \textbf{Regular day}\\
		\midrule
		\showrowcolors
		6 am – 9 am &  &  &  &  &  & \\
		& Not eating & 7655 & 31.2 & 0.129 & 0.45 & 0.32\\
		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.13 & 0.267 & 0.128\\
		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
		9 am – 12 am &  &  &  &  &  & \\
		& Not eating & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
		& Carbohydrate $\geqslant$ 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
		12 noon – 2 pm &  &  &  &  &  & \\
		& Not eating & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.56\\
		& Carbohydrate $\geqslant$ 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
		2 pm – 5 pm &  &  &  &  &  & \\
		& Not eating & 6926 & 28.3 & 0.13 & 0.123 & 0.659\\
		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
		& Carbohydrate $\geqslant$ 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
		5 pm – 8 pm &  &  &  &  &  & \\
		& Not eating & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.59 & 0.639\\
		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.37 & 0.211 & 0.328\\
		8 pm – 10 pm &  &  &  &  &  & \\
		& Not eating & 8722 & 35.6 & 0.322 & 0.291 & 0.48\\
		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
		& Carbohydrate $\geqslant$ 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
		10 pm – 6 am &  &  &  &  &  & \\
		& Not eating & 16295 & 66.6 & 0.68 & 0.59 & 0.751\\
		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
		& Carbohydrate $\geqslant$ 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
		\bottomrule
		\multicolumn{7}{l}{\textit{Note: }}\\
		\multicolumn{7}{l}{\textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed less }\\
		\multicolumn{7}{l}{than 50\% total energy intake.}\\ 
		\multicolumn{7}{l}{\textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed higher }\\
		\multicolumn{7}{l}{or equal to 50\% total energy intake.}\\ 
	\end{tabular}
\end{table}

@@

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

@@

>>>>

	\caption{\label{tab:daylevel}Day Level Latent Class Solution for Three-Class Model (No Individual level Model)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{llccccc}
		\hiderowcolors
		\toprule
		\textbf{Time slots of} & \textbf{Responses of} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(39.5\%)}} & \textbf{\Centerstack{Class 2\\(20.4\%)}} & \textbf{\Centerstack{Class 3\\(40.1\%)}} \\
		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}}\\
		\midrule
		\showrowcolors
		6 am – 9 am &  &  &  &  &  & \\
		& Not eating & 7655 & 31.2 & 0.129 & 0.450 & 0.320\\
		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.130 & 0.267 & 0.128\\
		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
		9 am – 12 am &  &  &  &  &  & \\
		& Not eating & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
		& Carbohydrate $\geqslant$ 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
		12 noon – 2 pm &  &  &  &  &  & \\
		& Not eating & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.560\\
		& Carbohydrate $\geqslant$ 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
		2 pm – 5 pm &  &  &  &  &  & \\
		& Not eating & 6926 & 28.3 & 0.130 & 0.123 & 0.659\\
		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
		& Carbohydrate $\geqslant$ 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
		5 pm – 8 pm &  &  &  &  &  & \\
		& Not eating & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.590 & 0.639\\
		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.370 & 0.211 & 0.328\\
		8 pm – 10 pm &  &  &  &  &  & \\
		& Not eating & 8722 & 35.6 & 0.322 & 0.291 & 0.480\\
		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
		& Carbohydrate $\geqslant$ 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
		10 pm – 6 am &  &  &  &  &  & \\
		& Not eating & 16295 & 66.6 & 0.680 & 0.590 & 0.751\\
		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
		& Carbohydrate $\geqslant$ 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
		\bottomrule
		\multicolumn{7}{l}{\textit{Note: }}\\
		\multicolumn{7}{l}{\textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed less }\\
		\multicolumn{7}{l}{than 50\% total energy intake.}\\ 
		\multicolumn{7}{l}{\textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed higher }\\
		\multicolumn{7}{l}{or equal to 50\% total energy intake.}\\ 
	\end{tabular}
\end{table}

@@

\begin{figure}
	%\vspace*{13cm}
	\centering
	\includegraphics{Figures/level1.png}
	\decoRule
	\caption[Day Level Latent Classes.]{Day Level Latent Classes.}
	\label{fig:level1}
\end{figure}
\vspace{-0.6cm}

%---------------------------------

--
%	SUBSECTION 2
%-----------------------------------

@@

\begin{figure}
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/level2.png}
	\decoRule
	\caption[Individual Level Latent Classes.]{individual Level Latent Classes.}
	\label{fig:level2}
\end{figure}
\vspace{-0.6cm}

### 2018-08-02 paper/Tables/2by2Table1.Rmd
level1 level2 fig added

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Daylevel.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "High carbohydrate day", "Low carbohydrate day", "Regular meals day", "P value [note]")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Characteristics of different types of days according to carbohydrate intake", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9)

### 2018-08-02 paper/Tables/2by2Table1.tex
level1 level2 fig added

>>>>

\caption{\label{tab:unnamed-chunk-6}Characteristics of different types of days according to carbohydrate intake}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{lllll}
\hiderowcolors
\toprule
  & High carbohydrate day & Low carbohydrate day & Regular meals day & P value [note]\\
\midrule
\showrowcolors
n & 9667 & 5002 & 9814 & \\
Country (\%) &  &  &  & <0.001\\
England & 5627 (58.2) & 2972 (59.4) & 5291 (53.9) & \\
NI & 1194 (12.4) & 527 (10.5) & 1400 (14.3) & \\
Scotland & 1527 (15.8) & 813 (16.3) & 1774 (18.1) & \\
Wales & 1318 (13.6) & 690 (13.8) & 1349 (13.7) & \\
Day of Week (\%) &  &  &  & <0.001\\
Monday & 1303 (13.5) & 715 (14.3) & 1370 (14.0) & \\
Tuesday & 1266 (13.1) & 674 (13.5) & 1290 (13.1) & \\
Wednesday & 1225 (12.7) & 740 (14.8) & 1233 (12.6) & \\
Thursday & 1272 (13.2) & 752 (15.0) & 1425 (14.5) & \\
Friday & 1458 (15.1) & 797 (15.9) & 1479 (15.1) & \\
Saturday & 1537 (15.9) & 703 (14.1) & 1495 (15.2) & \\
Sunday & 1605 (16.6) & 621 (12.4) & 1522 (15.5) & \\
Weekend, Yes (\%) & 3142 (32.5) & 1324 (26.5) & 3017 (30.7) & <0.001\\
Total energy (kJ) & 7539.98 (2875.87) & 7160.22 (2922.15) & 7439.68 (2978.91) & <0.001\\
Carbohydrate (g) & 222.79 (89.84) & 209.70 (86.17) & 206.59 (84.42) & <0.001\\
Protein (g) & 71.36 (29.79) & 69.55 (30.20) & 73.29 (32.94) & <0.001\\
Fat (g) & 65.44 (33.27) & 63.94 (33.76) & 67.24 (34.73) & <0.001\\
Alcohol (g) & 11.76 (27.31) & 8.85 (24.25) & 13.80 (33.00) & <0.001\\
Total sugars (g) & 98.63 (56.03) & 88.03 (50.50) & 86.39 (50.96) & <0.001\\
Starch (g) & 124.07 (55.84) & 121.59 (56.13) & 120.11 (54.62) & <0.001\\
Non-Milk Extrinsic Sugar (g) & 59.45 (49.31) & 50.07 (43.41) & 50.41 (44.84) & <0.001\\
Fruit (g) & 107.40 (137.97) & 103.15 (129.08) & 92.76 (126.02) & <0.001\\
Yellow Red Green Vegetables (g) & 26.52 (46.44) & 26.84 (47.99) & 26.16 (45.99) & 0.681\\
\bottomrule
\end{tabular}
\end{table}
